\section{Abstract}
\label{sec:abstract}

Link Prediction has been studied extensively in the recent years since many
communities such as  social networks and transportation networks benefit from
link prediction. Initially, only node based and path based similarity metrics
were used to predict links in graphs but eventually a diverse set of
supervised methods, probabilistic methods and non parametrical methods have
been designed for better performance. However there is no method which
performs better for all kinds of networks since each network has its unique set of
subnetworks which may be independent  or coevolving with each other. In some
cases, it could be difficult to model such networks,  making it
difficult to extract latent features. However, some networks such as social
networks and gaming  networks have been well studied and there are several off
the shelf methods which can be used to perform Link Prediction in them. 

In this paper, we take a specific gaming network called Travian dataset and
study a subset of all the methods which have used previously in related
networks to predict links. We also propose a redesigned version of an existing
algorithm  and compare it with the existing algorithms. Finally, we show that
in gaming networks,  algorithms which leverage cross layer information to
predict links in a target layer, thus  accounting for the effects of one layer
on another layer, perform better than the ones which  do not. Also, we show
that our proposed algorithm outperforms all the existinng algorithms.

\section{Keywords}

Link Prediction, Gaming Network, Multiplex Link Prediction, Dynamic Network.


