\section{Conclusion and Future Work}
\label{sec:conclusion}

In our fututre work, we want to apply and evaluate our algorithm on other
datasets such as social networks and research community networks. We want to
also work on improving the performance of our algorithm for performing dynamic
multiplex link prediction by incorporating more network features. This might
be cross intuitive as incorporating more features always does not provide with
better results for some datasets.  In the future we would also want to work on
modification of our reweighting procedure to account for negative cross layer
influences.

Currently, our implementation suffers from quadratic runtime bottlenecks on
the number of nodes in the overall graph. In the future, we hope to revamp our
code to use multiple cores instead of one through parallel processing of
sparse data structures that would decrease our load on the memory usage as
well. Due to the mathematical nature of our computations, our CPU usage shall
continue to be high.  Finally, our examined dataset was only a smalll snapshot
of the dataset. As the volume of dataset increases, we need to look for other
programming paradigms such as MapReduce if multithreading or multiprocessing
on a single-node falls short to keep the runtime linear with increase in load.
Leveraging the scalability of Apache GraphX over a cluster will be a start.
However, such decisions are still vague and will be motivated with further
research into not only such acyclic graphical models of computations such as
Spark, Dryad or Hadoop, but also having an indepth understanding of
combinatorial graph algorithms over big graphs.
